\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

\section{Bioinformatics Project
Proposal}\label{bioinformatics-project-proposal}

\subsection{Najib Ishaq}\label{najib-ishaq}

\subsubsection{Project Name}\label{project-name}

CASP (Critical Assessment of protein Structure Prediction)

This is a biennial competition in Bioinformatics where teams are tasked
with predicting the structure (among other things) of proteins given the
ammino-acid sequences.

\subsubsection{Outside Help}\label{outside-help}

\begin{itemize}
\tightlist
\item
  Course professors for what they know about protein folding.
\item
  My friend Tom Howard, should he have time, because we work very well
  together.
\item
  Strangers on the internet when I inevitably post on online forums
  asking questions about various snags I hit.
\end{itemize}

\subsubsection{Plan for the Project}\label{plan-for-the-project}

I will tackle structure prediction using various neural networks. My
plan so far is as follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Use convolutional layers, autoencoders, and other methods for feature
  extraction from the raw ammino acid sequence.
\item
  Feed the features to various types of networks to predict structure.
\end{enumerate}

As a baseline, I will use a convolutional neural network. I will then
try various combinations to enhance my performance. I will use the same
metrics that are used by the judges for the CASP competition.

My minimum goal for the semester will be to produce my baseline model
and at least three iterations of improvement upon it.

In addition to this minimum, I think I will be able to use Recurrent
Neural Networks to read the sequences and produce attention matrices
that help look at long-term dependencies of the structure on the
sequence.

As a lofty goal, something almost certainly outside my reach for this
semester, I will try to replicate what Google's DeepMind did for the
competition in 2018.

\subsubsection{Team Members}\label{team-members}

\begin{itemize}
\tightlist
\item
  Me.
\item
  Just me.
\end{itemize}

\subsubsection{Team Leader}\label{team-leader}

\begin{itemize}
\tightlist
\item
  I am the leader by default.
\end{itemize}

\subsubsection{Schedule}\label{schedule}

\begin{itemize}
\tightlist
\item
  One of the (occasional) downsides of being me is that I am forever
  saddled with my own company. Sometimes I amuse myself and at other
  times I frustrate myself. I will be in the lounge on floor 1 of Tyler
  on Wednesdays from 2pm to 5pm.
\item
  Please note that I too may drop in on any of you to ask questions
  about relevant topics, talk about life, and possibly share dark
  chocolate.
\end{itemize}

\subsubsection{Resources Needed}\label{resources-needed}

\begin{itemize}
\tightlist
\item
  I will read through several papers in the field. I have already
  started looked at the paper DeepMind released on AlphaZero. I am
  currently reading Dr.~Daniels' thesis.
\item
  I have my own GPU to run some serious computations but will likely
  need access to some better machines on campus. I already have accounts
  on Dr.~Daniels' machines will discuss specifics with him when I feel I
  have something that needs the extra computational power.
\item
  Any other resources that you think will be useful to me.
\end{itemize}

\end{document}
